\documentclass{article}

\usepackage[paperwidth=8cm, paperheight=5cm, hmargin=0mm, 
    top=0mm, bottom=0mm] {geometry}


\pagestyle{empty}



\begin{document}

This is a test. This is a longer sentence with some more words, isn't it? This is a test. This is a longer sentence with some more words, isn't it? This is a test. This is a longer sentence with some more words, isn't it?

This is a test:
\begin{itemize}
\item Hello

\item This is a test. This is a longer sentence with some more words, isn't it? This is a test. This is a longer sentence with some more words, isn't it? This is a test.

\item Good Bye

\item Hello

\item This is a test. This is a longer sentence with some more words, isn't it? This is a test. This is a longer sentence with some more words, isn't it? This is a test.
\end{itemize}

This is a test. This is a longer sentence with some more words, isn't it? This is a test. This is a longer sentence with some more words, isn't it? This is a test. This is a longer sentence with some more words, isn't it? This is a test. This is a longer sentence with some more words, isn't it? This is a test. This is a longer sentence with some more words, isn't it? This is a test. This is a longer sentence with some more words, isn't it? This is a test. This is a longer sentence with some more words, isn't it? This is a test. This is a longer sentence with some more words, isn't it? This is a test. This is a longer sentence with some more words, isn't it? This is a test. This is a longer sentence with some more words, isn't it? This is a test. This is a longer sentence with some more words, isn't it? This is a test. This is a longer sentence with some more words, isn't it?

This is a test. This is a longer sentence with some more words, isn't it? This is a test. This is a longer sentence with some more words, isn't it? This is a test. This is a longer sentence with some more words, isn't it? This is a test. This is a longer sentence with some more words, isn't it?

This is a test. This is a longer sentence with some more words, isn't it? This is a test. This is a longer sentence with some more words, isn't it? 
\end{document}